Adversarial Training of Invariant Features for Speech Recognition

### 2017-03-21 interspeech/paper.tex

% This is more of an explanation of the method rather than a literature review.
    % Perhaps we should change the section title.
\section{Background}
\label{sec:background}
\begin{figure*}
    \centering

@@

    % dima: I want to add something like this:
    %Another point of view on the GAN training is that the generator is matching
    %the distribution of the data with the distribution of the generator using
    %a discriminator to provide the training signal. This approach can be generalized
    %on any distributions to be matched.
    Prior work by~\cite{ganin2014unsupervised} proposed a method for training a network 
    which can be adapted to new domains. The training data consists of the images
    labeled with classes of interest and separate domain (image background) labels. 
    The network has a $Y$-like structure: the image is fed to the
    first network which produces a hidden representation $h$. Then this 
    representation $h$ is input to two separate networks: a domain classifier network (D) and 
    a target classifier network (R). The goal of training is to learn a hidden 
    representation that is invariant to the domain labels and still performs well on 
    the target classification task, so that the domain information doesn't 
    interfere with the target classifier at test time. Similar to the GAN 
    objective, which forces the generation distribution be close to the data distribution,
    the \emph{gradient reverse method} makes domain specific distributions similar to each other.

@@

For both the clean and noisy data, we extracted 40-dimensional Mel-filterbank features with their deltas and 
delta-deltas spliced over $\pm$5 frames, resulting in 1320 input 
features that were subsequently mean and variance normalized. The baseline
acoustic model was a 6-layer 
DNN with 2048 rectified linear units at every layer. It was trained using 
momentum-accelerated stochastic gradient descent for 15 epochs with new-bob 
annealing~\citep[half the learning rate if no improvement on the validation set, as in][]{morgan1995continuous,sainath2011making}.

To evaluate the impact of our method on generalization to unseen noises,
we performed 6 experiments with different sets of noises seen during training.
The networks were trained
on clean data, with each noise condition added one-by-one in the following order: airport, babble, car, 
restaurant, street, and train. The last training group included all noises and therefore matched the
standard multi-condition training setup. For every training group, we trained the
baseline and the invariance model, where we branched out at the $4^{th}$ layer to a
binary classifier predicting clean versus noisy data. Due to the imbalance between amounts of clean and
noisy utterances, we had to oversample noisy frames to ensure that every mini-batch contained
equal number of clean and noisy speech frames.

Table~\ref{tab:results} summarizes the results. Figure~\ref{fig:results} visualizes 
the word error rate (WER) for the baseline multi-condition training and invariance training 
as the number of seen noise types varies. We conclude that the best performance
gain is achieved when a small number of noise types are available during training. 
It can be seen that invariance training is able to generalize better to unseen 
noise types compared with multi-condition training.

>>>>

\section{Background}
\label{sec:background}
\begin{figure*}
    \centering

@@

    %TODO
    % dima: I want to add something like this:
    %Another point of view on the GAN training is that the generator is matching
    %the distribution of the data with the distribution of the generator using
    %a discriminator to provide the training signal. This approach can be generalized
    %on any distributions to be matched.
    Prior work by~\cite{ganin2014unsupervised} proposed a method for training a network 
    which can be adapted to new domains. The training data consists of the images
    labeled with classes of interest and separate domain (image background) labels. 
    The network has a $Y$-like structure: the image is fed to the
    first network which produces a hidden representation $h$. Then this 
    representation $h$ is input to two separate networks: a domain classifier network (D) and 
    a target classifier network (R). The goal of training is to learn a hidden 
    representation that is invariant to the domain labels and still performs well on 
    the target classification task, so that the domain information doesn't 
    interfere with the target classifier at test time. Similar to the GAN 
    objective, which forces the generation distribution be close to the data distribution,
    the \emph{gradient reverse method} makes domain specific distributions similar to each other.

@@

For both the clean and noisy data, we extracted 40-dimensional Mel-filterbank features with their deltas and 
delta-deltas spliced over $\pm$5 frames, resulting in 1320 input 
features that were subsequently mean and variance normalized. The baseline
acoustic model was a 6-layer 
DNN with 2048 rectified linear units at every layer. It was trained using 
momentum-accelerated stochastic gradient descent for 15 epochs with new-bob 
annealing~\citep[the learning rate is halfed if no improvement on the validation set, as in][]{morgan1995continuous,sainath2011making}.

% TODO
% dima: we need to emphasize that the unseen noises are very important
To evaluate the impact of our method on generalization to unseen noises,
we performed 6 experiments with different sets of noises seen during training.
The networks were trained
on clean data, with each noise condition added one-by-one in the following order: airport, babble, car, 
restaurant, street, and train. The last training group included all noises and therefore matched the
standard multi-condition training setup. For every training group, we trained the
baseline and the invariance model, where we branched out at the $4^{th}$ layer to a
binary classifier predicting clean versus noisy data. Due to the imbalance between amounts of clean and
noisy utterances, we had to oversample noisy frames to ensure that every mini-batch contained
equal number of clean and noisy speech frames.

Table~\ref{tab:results} summarizes the results. Figure~\ref{fig:results} visualizes 
the word error rate (WER) for the baseline multi-condition training and invariance training 
as the number of seen noise types varies. We conclude that the best performance
gain is achieved when a small number of noise types are available during training. 
It can be seen that invariance training is able to generalize better to unseen 
noise types compared with multi-condition training.
% dima: we need to add that this is good news and very reasonable
